Mathematical appendix to "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2022-07-12 src/docs_paper/appendix.Rmd
Model selection note #128

We performed model selection on the basis of the conditional predictive ordinate (CPO) criterion [@pettit1990conditional].
For comparison, we also calculated the deviance information criterion (DIC) [@spiegelhalter2002bayesian] and widely applicable information criterion (WAIC) [@watanabe2013widely].

>>>>

We performed model selection on the basis of the conditional predictive ordinate (CPO) criterion [@pettit1990conditional], selecting model M2.
This model included Besag spatial random effects and IID temporal random effects.
The deviance information criterion (DIC) [@spiegelhalter2002bayesian] and widely applicable information criterion (WAIC) [@watanabe2013widely] are included for reference (Table \ref{tab:multinomial-model-performance} and Figure \ref{fig:multinomial-model-performance}).
